---
title: 'Regression'
author: "Xingyan"
date: "2025-04-11"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=F}
library(dplyr)
library(tidyr)
library(knitr)
library(gtsummary)
library(cobalt)
library(stargazer)
library(stringr)
library(sandwich)
library(lmtest)


data <- readr::read_csv("../data/processed/full_data_cleaned.csv")

```

## Balance Test

### Method

Include demographic information, trust towards social media and vaccination baseline information in balance test. 

### Result

There is no significant imbalance across treatment and control arms. Treatment and control groups are randomly assigned.

```{r}
factor_vars <- c("age", "gender", "race", "ethnicity", "income", "education", "political_belief", "urbanicity","social_media_trust","vaccination_intention","vaccine_doses", "state")
data <- data %>%
  mutate(across(all_of(factor_vars), as.factor))

# Create summary table with balance tests
balance_table <- dplyr::select(data,
                               ad_group, age, gender, race, ethnicity, income, education, 
                               political_belief, urbanicity,
                               social_media_trust, vaccination_intention, vaccine_doses, state) %>%
  tbl_summary(
    by = ad_group,
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    digits = all_categorical() ~ c(0, 1)
  ) %>%
  add_p(test = list(all_categorical() ~ "chisq.test",
                   all_continuous() ~ "aov")) %>%
  modify_header(label = "**Variable**") %>%
  modify_spanning_header(c("stat_1", "stat_2", "stat_3") ~ "**Treatment Group**") %>%
  bold_labels()


#Save balance test table 
balance_gt <- balance_table %>% 
  as_gt() %>%
  gt::tab_header(
    title = "Balance Across Treatment Groups"
  )

gt::gtsave(
  data = balance_gt,
  filename = here::here("output", "tables", "balance_test.html"),
  inline_css = TRUE
)

balance_table

```

## Regression 

### Hypotheses 

H1a: Emotion ads will significantly increase vaccine uptake.

H1b: Reason ads will significantly increase vaccine uptake. 

### Result
Both hypotheses about ad effectiveness were strongly supported:

**H1a: Emotion ads increase vaccine uptake**  
- All models show large, highly significant positive effects (β = 1.35 to 1.48, p < 0.001)
- Odds ratios of e<sup>1.45</sup> ≈ 4.26 indicate emotion ad recipients had 4.26 times higher odds of getting additional doses than control

**H1b: Reason ads increase vaccine uptake**  
- Consistent positive effects across models (β = 0.94 to 1.02, p < 0.001)
- Smaller effect than emotion ads (e<sup>0.94</sup> ≈ 2.56 times higher odds)

**Demographic Pattern**  
There is limited evidence for demographic moderators, which suggest emotion/reason ads worked similarly across most subgroups. 

```{r}
# Remove Rows with any "Prefer not to say" Responses
target_cols <- c("age", "gender", "race", "ethnicity", "income", "education", "political_belief", 
                 "covid_positive", "vaccine_doses", "chronic_condition")

df <- data %>% filter(if_all(all_of(target_cols),~!str_detect(.x, fixed("Prefer not to say", ignore_case = TRUE)))) 
```

```{r}
#Prepare variables for regression modeling 
df <- df %>% 
  mutate(additional_doses = as.numeric(additional_doses == "Yes"),
         age = factor(age, levels = c("13-17", "18-29", "30-49", "50-64", "65+")),
         gender = factor(gender, levels = c("Female","Male")),
         race = factor(race, levels = c("White", "Black or African American", "Asian", "American Indian or Alaska Native", "Native Hawaiian or Pacific Islander", "Other" )),
         urbanicity = factor(urbanicity, levels = c("Urban","Rural")),
         income = factor(income, levels = c("<$30K", "$30K-$69,999", "$70K-$99,999", ">100k")),
         education = factor(education,levels = c("High school or Less", "Some college", "College +", "Prefer not to say")),
         political_belief = factor(political_belief, levels = c("Conservative","Moderate","Liberal"))
         )
``` 

```{r}
models <- list(
  "Model 1" = glm(additional_doses ~ ad_group, 
                 data = df, family = binomial),
  
  "Model 2" = glm(additional_doses ~ ad_group + race + political_belief + urbanicity + 
                  ad_group*race,
                 data = df, family = binomial),
  
  "Model 3" = glm(additional_doses ~ ad_group + race + political_belief + urbanicity + 
                  ad_group*political_belief,
                 data = df, family = binomial),
  
  "Model 4" = glm(additional_doses ~ ad_group + race + political_belief + urbanicity + 
                  ad_group*urbanicity,
                 data = df, family = binomial)
)

#Standard errors clustered by state in parentheses
clustered_models <- lapply(models, function(m) {
  coeftest(m, vcov = vcovCL(m, cluster = ~state, type = "HC1"))
})

output_file <- here::here("output", "tables", "regression_results.html")

stargazer(models,
          se = lapply(clustered_models, function(x) x[, "Std. Error"]),
          p = lapply(clustered_models, function(x) x[, "Pr(>|z|)"]),
          type = "html",
          out = output_file,
          title = "Impact of Each Treatment Arm on Additional Vaccination Dose",
          column.labels = names(models),
          covariate.labels = c(
            "Emotion Ad", "Reason Ad",
            "Black/African American", "Asian","American Indian or Alaska Native", "Native Hawaiian or Pacific Islander", "Other Race", "Moderate","Liberal", "Rural", "Black/African America × Emotion", "Black/African America × Reason", "Asian× Emotion","Asian× Reason", "American Indian or Alaska Native × Emotion", "American Indian or Alaska Native × Reason", "Native Hawaiian or Pacific Islander × Emotion", "Native Hawaiian or Pacific Islander × Reason", "Other Race × Emotion", "Other Race × Reason", "Moderate × Emotion","Moderate × Reason", "Liberal × Emotion","Liberal × Reason", "Rural × Emotion","Rural × Reason"
          ),
          model.numbers = FALSE,
          notes = c("Standard errors clustered by state in parentheses",
                   "*** p<0.01, ** p<0.05, * p<0.1")
          )


```


